### 2023-05-08 Documentation/UFMG/PFCII/LiteratureReview/LiteratureReview.tex
documentation

\begin{figure}[H]
  \centering
  \resizebox{80mm}{!}{\includegraphics{Figuras/ehda_ex_2.png}}
  \caption{EHDA physical concept \cite{Gabriel}}
  \label{fig:ehda_setup_ex2}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \resizebox{100mm}{!}{\includegraphics{Figuras/system_setup.png}}
  \caption{EHDA experiment setup \cite{Luewton}}
  \label{fig:ehda_setup}
\end{figure}

@@

\begin{figure}[H]
  \center
  \includegraphics[width=3cm]{Figuras/19:03/drip_example.png}
  \label{fig:drip_example}
  \caption{Dripping}
\end{figure}

@@

  \begin{figure}[H]
      \center
      \includegraphics[width=15cm]{Figuras/19:03/intermittent_example.png}
      \label{fig:intermittent_example}
      \caption{Intermittent examples}
  \end{figure}

@@

  \begin{figure}[H]
      \center
      \includegraphics[width=15cm]{Figuras/april/conjet.png}
      \label{fig:conjt}
      \caption{Cone Jet}
  \end{figure}

@@

In recent times, researchers have made significant advancements in understanding multi-jet technology and have identified various profiles with distinct characteristics. Because of that, some authors can divide what we call multi jet in more classifications.
The multi jet mode is considered in this work when two or more spraying jets can be visualized in the HS camera and the current shows a stable profile. Figures \ref{fig:multijt1}, \ref{fig:multijt2} and \ref{fig:multijt3} shows three different variations of multi jet spraying mode.

C.N. Ryan (2012)\cite{Ryan} focused his work in multi jet spraying mode, and its current properties. 
He detected that for a low number of jets emitted, seen in figure \ref{fig:multijt}, the meniscus is not bound to the rim of the capillary. 
This mode is seen to be less stable, in that each jet in multi-jet mode is unable to support the same volumetric flow as in the single jet mode.
As the number of jets increases the mode becomes what Ryan refers at rim-mode electrospray. 
In this work, all modes with more than one stable jet will be classified as multi jet.

  \begin{figure}[H]
      \center
      \includegraphics[width=15cm]{Figuras/april/multjt.png}
      \label{fig:multijt}
      \caption{Multi Jet}
  \end{figure}

>>>>

\begin{figure}[H]
  \centering
  \resizebox{80mm}{!}{\includegraphics{Figuras/ehda_ex_2.png}}
  \caption{EHDA physical concept\cite{Gabriel}.}
  \label{fig:ehda_setup_ex2}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \resizebox{100mm}{!}{\includegraphics{Figuras/system_setup.png}}
  \caption{EHDA experiment setup\cite{Luewton}.}
  \label{fig:ehda_setup}
\end{figure}

@@

\begin{figure}[H]
  \center
  \includegraphics[width=3cm]{Figuras/19:03/drip_example.png}
  \label{fig:drip_example}
  \caption{Dripping examples.}
\end{figure}

@@

  \begin{figure}[H]
      \center
      \includegraphics[width=15cm]{Figuras/19:03/intermittent_example.png}
      \label{fig:intermittent_example}
      \caption{Intermittent examples.}
  \end{figure}

@@

  \begin{figure}[H]
      \center
      \includegraphics[width=15cm]{Figuras/april/conjet.png}
      \label{fig:conjt}
      \caption{Cone Jet examples.}
  \end{figure}

@@

In recent times, researchers have made significant advancements in understanding multi-jet technology and have identified various profiles with distinct characteristics. Because of that, some authors can divide what we call multi jet in more classifications.
The multi jet mode is considered in this work when two or more spraying jets can be visualized in the HS camera and the current shows a stable profile.

C.N. Ryan (2012)\cite{Ryan} focused his work in multi jet spraying mode, and its current properties. 
He detected that for a low number of jets emitted the meniscus is not bound to the rim of the capillary. 
This mode is seen to be less stable, in that each jet in multi-jet mode is unable to support the same volumetric flow as in the single jet mode.
As the number of jets increases the mode becomes what Ryan refers at rim-mode electrospray. 
In this work, all modes with more than one stable jet will be classified as multi jet. Figure \ref{fig:multijt} shows three different variations of multi jet spraying mode.

  \begin{figure}[H]
      \center
      \includegraphics[width=15cm]{Figuras/april/multjt.png}
      \label{fig:multijt}
      \caption{Multi Jet examples.}
  \end{figure}
